---
title: "References"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{References}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(simpleEnsembleGroup11)
```


```{r}
citation("glmnet")
```
1. Friedman, J., Hastie, T., & Tibshirani, R. (2010). *Regularization Paths for Generalized Linear Models via Coordinate Descent*. Journal of Statistical Software, 33(1), 1-22.  
2. https://glmnet.stanford.edu/articles/glmnet.html

```{r}
citation("randomForest")
```
3. Liaw, A., & Wiener, M. (2002). *Classification and Regression by randomForest*. R News, 2(3), 18-22.
4. Wright, M. N., & Ziegler, A. (2017). *ranger: A Fast Implementation of Random Forests for High Dimensional Data in C++ and R*. Journal of Statistical Software, 77(1), 1-17.

### Ensemble Learning

5. Gashler, M., & Martinez, T. (2017). *Decision Tree Ensemble: Small Heterogeneous Is Better Than Large Homogeneous*. In Seventh International Conference on Learning Representations (ICLR). 
6. Guyon, I., & Elisseeff, A. (2003). *An introduction to variable and feature selection*. Journal of Machine Learning Research, 3, 1157-1182.
7. Dietterich, T. G. (2000). *Ensemble methods in machine learning. In International workshop on multiple classifier systems (pp. 1-15)*. Springer, Berlin, Heidelberg.

## Building and Documenting R Packages

### Package development

8. Wickham, H., & Bryan, J. (2019). *R Packages: Organize, Test, Document, and Share Your Code, 2nd Edition*. O'Reilly Media.
9. https://r-pkgs.org/description.html
10. https://tinyheero.github.io/jekyll/update/2015/07/26/making-your-first-R-package.html

### Documentation and Vignettes

11. https://kbroman.org/pkg_primer/pages/depends.html
12. Xie, Y., Allaire, J.J., & Grolemund, G. (2018). *R Markdown: The Definitive Guide*. Chapman and Hall/CRC.


